A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-24 paper/paper.tex
paper: fix a typo
explaining the recursion argument already in itt

Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$. This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule. Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$. This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$. Even though it looks independent of the other tables, it has to proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions.

@@

For a fixed $n$, $\framep$, $\restrf$, and $\cohf$ have to be mutually defined by induction on $p$. Each of them rely on $\painting$, $\restrc$, and $\cohc$ at lower $n$, so they are well-founded. Finally, each of $\painting$, $\restrc$, and $\cohc$ are built by induction from $p$ to $n$.

>>>>

Notably, the definition of $\restrl$ relies on a definitional equality expressing the commutation of the composition of $\restrf$. This commutation is not provable by computation so we have to prove it propositionally before using the reflection rule. Proving this itself requires an induction on the dimension, and on the structure of $\framep$, $\layer$, and $\painting$. This is what $\cohf$ proves, as shown in the table \ref{tab:coh}, using auxiliary definitions $\cohl$ and $\cohc$. Even though it looks independent of the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions. More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be mutually defined by induction on $p$. Similarly, the block made of $\painting$, $\restrc$, and $\cohc$ is built by induction from $p$ to $n$. The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but, conversely, the dependency is only on lower $n$, so this is well-founded. Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations. We leave however here implicit the exact way this mutual recursion can be formalized.

@@

The way recursion is implemented is still left implicit at this stage. See \ref{sec:mech} for the details.
